Clustering exploration for `r params$library_id`

### 2024-11-20 analyses/cell-type-ewings/template_notebooks/clustering-workflow/01-clustering-metrics.Rmd
use different resolution for cpm

# leiden clustering
leiden_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "leiden",
  nn = seq(5, 40, 5),
  resolution = c(0.5, 1, 1.5),
  objective_function = c("CPM", "modularity")
) |> 
  dplyr::bind_rows()
```

```{r}
# join all clustering results 
all_cluster_results <- dplyr::bind_rows(list(louvain_results, leiden_results)) |> 
  # add column for method + objective function 
  # use this for splitting plots throughout report
  dplyr::mutate(cluster_method = glue::glue(
    "{algorithm}-{objective_function}"
  ) |> 
    stringr::str_remove("-NA")
  )
```

>>>>

# leiden cpm clustering
leiden_cpm_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "leiden",
  nn = seq(5, 40, 5),
  resolution = c(0.001, .005, .01),
  objective_function = "CPM"
) |> 
  dplyr::bind_rows()

# leiden modularity clustering
leiden_mod_results <- rOpenScPCA::sweep_clusters(
  sce,
  algorithm = "leiden",
  nn = seq(5, 40, 5),
  resolution = c(0.5, 1, 1.5),
  objective_function = "modularity"
) |> 
  dplyr::bind_rows()
```

```{r}
# join all clustering results 
all_cluster_results <- dplyr::bind_rows(list(louvain_results, leiden_cpm_results, leiden_mod_results)) |> 
  # add column for method + objective function 
  # use this for splitting plots throughout report
  dplyr::mutate(cluster_method = glue::glue(
    "{algorithm}-{objective_function}"
  ) |> 
    stringr::str_remove("-NA")
  )
```
